---
title: 'Chapter 4: 4.3, 4.7, 4.13, 4.18, 4.22'
author: "Jeremy Ling & Emmanuel Mejia"
date: "March 27, 2018"
output: pdf_document
---

##4.3

```{r cache=FALSE, results=FALSE, warning=FALSE, comment=FALSE, warning=FALSE}
library(readxl)
cloth <- read_excel("cloth.xlsx")



clothLong=reshape(cloth,
                     varying = c("Bolt1", "Bolt2", "Bolt3",
                                 "Bolt4", "Bolt5"),
                     v.names = "Yield", timevar = "Bolt",
                     direction = "long")

```

```{r}
cloth.aov=aov(Yield ~ factor(Bolt) + factor(Chemical), data = clothLong)
summary(cloth.aov)
MSe=summary(cloth.aov)[[1]][3,3]
```

$H_0: T_1=...=T=p=0$

vs

$H_1: T_i\ne 0$ at least one.

From our ANOVA we see that our chemical has an f-value of 2.376 with a p-value = 0.121. Our p-value is too big so we must fail to reject our null hypothesis and conclude that there is no differences between the treatment/chemical types.

##4.7

```{r cache=FALSE, results=FALSE, warning=FALSE, comment=FALSE, warning=FALSE}
library(readxl)
cscale <- read_excel("cscale.xlsx")

cscaleLong=reshape(cscale,
                     varying = c("Coupon1", "Coupon2", "Coupon3",
                                 "Coupon4"),
                     v.names = "Yield", timevar = "Coupon",
                     direction = "long")

```

(a)

```{r}
cscale.aov=aov(Yield ~ factor(Coupon) + factor(Tip), data = cscaleLong)
summary(cscale.aov)
MSe=summary(cscale.aov)[[1]][3,3]
```

$H_0: T_1=...=T=p=0$

vs

$H_1: T_i\ne 0$ at least one.

Based on our ANOVA we see that we have a f-value of 14.44 and a p-value of 0.000871. Our p-value is very small compare to the significance value so we must reject our null hypothesis and conclude that the treatment/tips are significantly different. 

(b)

```{r}
ybar.trt=as.vector(with(cscaleLong, tapply(Yield,Tip,function(x) mean(x)))) #bar(Y_i.) vector

#1-2
a=4;b=4;N=a*b;alpha=0.05
t0=(ybar.trt[1]-ybar.trt[2])/sqrt(2*MSe/b)
cri=qt(alpha/2,(a-1)*(b-1),lower.tail=F)
pvalue=2*pt(abs(t0),(a-1)*(b-1),lower.tail=F); pvalue
#1-3
a=4;b=4;N=a*b;alpha=0.05
t0=(ybar.trt[1]-ybar.trt[3])/sqrt(2*MSe/b)
cri=qt(alpha/2,(a-1)*(b-1),lower.tail=F)
pvalue=2*pt(abs(t0),(a-1)*(b-1),lower.tail=F); pvalue
#1-4
a=4;b=4;N=a*b;alpha=0.05
t0=(ybar.trt[1]-ybar.trt[4])/sqrt(2*MSe/b)
cri=qt(alpha/2,(a-1)*(b-1),lower.tail=F)
pvalue=2*pt(abs(t0),(a-1)*(b-1),lower.tail=F); pvalue
#2-3
a=4;b=4;N=a*b;alpha=0.05
t0=(ybar.trt[2]-ybar.trt[3])/sqrt(2*MSe/b)
cri=qt(alpha/2,(a-1)*(b-1),lower.tail=F)
pvalue=2*pt(abs(t0),(a-1)*(b-1),lower.tail=F); pvalue
#2-4
a=4;b=4;N=a*b;alpha=0.05
t0=(ybar.trt[2]-ybar.trt[4])/sqrt(2*MSe/b)
cri=qt(alpha/2,(a-1)*(b-1),lower.tail=F)
pvalue=2*pt(abs(t0),(a-1)*(b-1),lower.tail=F); pvalue
#3-4
a=4;b=4;N=a*b;alpha=0.05
t0=(ybar.trt[3]-ybar.trt[4])/sqrt(2*MSe/b)
cri=qt(alpha/2,(a-1)*(b-1),lower.tail=F)
pvalue=2*pt(abs(t0),(a-1)*(b-1),lower.tail=F); pvalue
```

While using Fisher LSD we output a pvalue for the compariosns of $\mu_1=\mu_2$, $\mu_1=\mu_3$, $\mu_1=\mu_4$, $\mu_2=\mu_3$, $\mu_2=\mu_4$, and $\mu_3=\mu_4$ and the results are presented above respectively. We see that the comparisons of $\mu_1=\mu_4$, $\mu_2=\mu_4$, and $\mu_3=\mu_4$ are different in tips of mean hardness.

(c)

```{r fig.width=4, fig.height=3}
cscale.lm=lm(Yield ~ factor(Tip), data = cscaleLong)
summary(cscale.lm)

library(car)
qqPlot(residuals(cscale.lm))
plot(fitted(cscale.lm), residuals(cscale.lm))
plot(fitted(cscale.lm), abs(residuals(cscale.lm)))
```

After observing the qqplot and residual plot we see that normality is fine and there is no pattern but a structureless image on our plot. We can conclude our model is good.

##4.13

```{r}
library(readxl)
latin <- read_excel("latin.xlsx")
matrix(latin$SD, 4,6)
matrix(latin$Voltage, 4,6)
```

(a)

```{r}
summary(aov(Voltage ~ factor(Ratio.Control) + factor(Time.Period) + SD, latin))
```

$H_0: T_1=...=T=p=0$

vs

$H_1: T_i\ne 0$ at least one.

We look at our ANOVA and pay close attention to our results in terms of ratio control. We have a f-value of 0.191 and a p-value too big of 0.901. We fail to reject our null hypothesis and conclude that ratio control has no affect on voltage.

(b)

```{r}

```